---
title: "Plotly"
author: "Amy Yeung"
date: "2022-10-25"
output: 
  html_document:
    toc: true
    toc_float: true
  
---

We're going to make some plotly plots.

## Load packages and data


```{r, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

Let's get some data.

```{r}
data("nyc_airbnb")

nyc_airbnb = nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>% 
  select(borough = neighbourhood_group, neighbourhood, price, room_type, lat, long, rating) %>% 
  filter(
    borough == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500
  ) %>% 
  drop_na(rating)
```

Let's make a scatterplot!

```{r}
nyc_airbnb %>% 
  mutate(
    text_label = str_c("Price: ", price, "\nRating: ", rating)
  ) %>% 
  plot_ly(
    x = ~lat, # ~ indicates lat is a variable
    y = ~long,
    color = ~price,
    type = "scatter", mode = "markers",
    alpha = 0.5,
    text = ~text_label
  )
```


Let's make boxplots

```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood,
          type = "box", colors = "viridis")
```

Can we make a bar plot?

```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(
    x = ~neighbourhood, y = ~n,
    type = "bar")
```


## ggplotly

```{r}
ggp_scatterplot = nyc_airbnb %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()

ggplotly(ggp_scatterplot) 
# slower to interact, a bit uglier, but useful if you want to use ggplot by yourself first
# plot_ly is still superior if sharing with others
```

## Create a dashboard
But dashboards are a standalone thing - need to do them separately
If you were to move it within the github.io (website) repo, it becomes part of the website - need to build website to get right formatting.
Can also do a more specific command: `rmarkdown::render("dashboard_name.Rmd", output_format = "flexdashboard::flex_dashboard")`




